### 2016-03-21 manuscript.Rnw
incorporate Ross's comments on pre-print

Ideally, the ever increasing number of published phylogenies would contribute to
a synthesis of phylogenetic knowledge, ultimately leading to a better
understanding of the history of life while at the same time providing
high-quality phylogenetic information for use in comparative analyses. However,
in practice, synthesizing phylogenetic data is a difficult task. Phylogenetic
information is largely scattered, often only available as image files within
publications, and the lack of standardization to store and represent
phylogenetic data makes it difficult for researchers to access, synthesize, and
integrate this information into their own research (\citealt{Stoltzfus2012};
\citealt{Drew2013}; but see \citealt{Cranston2014} for suggestions of best
practices).

@@

These packages, combined with the language's support for literate programming
(\citealt{Knuth1984}; \citealt{Xie2014}), make R an ideal platform for
reproducible research in phylogenetics and comparative biology, as they allow a
complete record of the steps taken in gathering, processing, and analyzing a
given data set to be produced.

>>>>

Ideally, the ever increasing number of published phylogenies would contribute to
a synthesis of phylogenetic knowledge, ultimately leading to a better
understanding of the history of life while at the same time providing
high-quality phylogenetic information for use in comparative analyses. However,
in practice, synthesizing phylogenetic data is a difficult task. Phylogenetic
information is largely scattered, often only available as image files within
publications, and the lack of standardization to store and represent
phylogenetic data makes it difficult for researchers to access, synthesize, and
integrate this information into their own research (\citealt{Stoltzfus2012,
  Drew2013, Magee2014}; but see \citealt{Cranston2014} for suggestions of best
practices).

@@

These packages, combined with the language's support for literate programming
(\citealt{Knuth1984}; \citealt{Xie2014}), make R a comprehensive platform for
reproducible research in phylogenetics and comparative biology, as they allow a
complete record of the steps taken in gathering, processing, and analyzing a
given data set to be produced.
